---
title: "Daily Schedule"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

<button class="accordion">Before Starting the Program</button>
<div class="panel"> 

| To-Do         |                              | 
|---------------|------------------------------------|
| Download and Install R | [Link](https://mirror.las.iastate.edu/CRAN/) [Video](https://uci.yuja.com/V/Video?v=3173351&node=10757512&a=280036139&autoplay=1)|
| Download and Install RStudio| [Link](https://www.rstudio.com/products/rstudio/download/)  [Video](https://uci.yuja.com/V/Video?v=3173359&node=10757552&a=664679852&autoplay=1)|
|Setup RStudio| [Video](https://uci.yuja.com/V/Video?v=3173384&node=10757676&a=717681262&autoplay=1)       |
|Download packages |<a href="R-code/code-00-setup.R" download>File</a> [Video](https://uci.yuja.com/V/Video?v=3173415&node=10757778&a=1269482034&autoplay=1)|
|Alzheimer's Disease | [Slides](https://cosmos-datascience.github.io/slides/week01/2023_Intro_to_AD_Online.pdf) |

</div>


<!-- connecting to UCI email address-->
		
<button class="accordion">Day 1 &#9679; July 6 &#9679; What is Data Science? </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 09:30 | Welcome                            |[Slides](https://cosmos-datascience.github.io/slides/week01/01a-welcome.html)|
| 09:35 - 10:30 | Introduction to data science    |[Slides](https://cosmos-datascience.github.io/slides/week01/01b-intro-data-science.html){target="_blank"}|
| 10:45 - 11:45 | Introduction to R, RStudio, and Quarto    |[Slides](https://cosmos-datascience.github.io/slides/week01/01c-intro-R.pdf){target="_blank"}|
| 1:00 - 3:00 | Lab practice |[Slides](https://cosmos-datascience.github.io/slides/week01/2026-qmds/Lab-1-intro-R.html){target="_blank"}|

<!--
| 2:00 - 3:00 | Introduction to GitHub    |[Slides](https://cosmos-datascience.github.io/slides/week01/Lab-01c-github.html)|
-->

</div>
		




<button class="accordion">Day 2 &#9679; July 7 &#9679; Exploratory Data Analysis </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 9:30 | R Packages                            |[Slides]( https://cosmos-datascience.github.io/slides/week01/02a-R-packages.html ){target="_blank"} |
| 09:30 - 10:00 | Data in R                            |[Slides]( https://cosmos-datascience.github.io/slides/week01/02b-R-Data.html ){target="_blank"} |
| 10:20 - 11:45 | Describing data and EDA    |[Slides](https://cosmos-datascience.github.io/slides/week01/02c-EDA.html){target="_blank"}|
| 1:00 - 2:00 | Intro to Tidyverse              | [Slides](https://cosmos-datascience.github.io/slides/week01/Lab-02c-intro-tidyverse.html){target="_blank"}|
| 2:15 - 3:00 | Intro to Data Wrangling              | [Slides](https://cosmos-datascience.github.io/slides/week01/Lab-02d-intro-data-wrangling.html){target="_blank"}|
</div>
	
	

<button class="accordion">Day 3 &#9679; July 8 &#9679; Probability </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 11:50 | Introduction to probability                           |[Slides](https://cosmos-datascience.github.io/slides/week01/03a-intro-prob.html){target="_blank"}|
</div>
		



<button class="accordion">Day 4 &#9679; July 9 &#9679; Estimation </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 11:45 | Point estimation and confidence interval      |[Slides](https://cosmos-datascience.github.io/slides/week01/04a-estimation.html){target="_blank"} |
| 1:00 - 1:50 | Data visualization in R |[Slides](https://cosmos-datascience.github.io/slides/week01/Lab-04a-visualize-data.html){target="_blank"}|
| 2:00 - 3:50 | Advanced Data visualization in R |[Slides](https://cosmos-datascience.github.io/slides/week01/Lab-04b-adv-visualize-data.html){target="_blank"}|

</div>
	
	


<button class="accordion">Day 5 &#9679; July 10 &#9679; Hypothesis testing </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 9:00 - 10:30 | Hypothesis testing I                       |<!--[Slides](https://cosmos-datascience.github.io/slides/week01/05a-hypothesis-Quarto.html)--> |
| 10:45 - 12:00 | Hypothesis testing II |<!--[Slides](https://cosmos-datascience.github.io/slides/week01/05b-hypothesis-Quarto.html)-->|
| 1:00 - 2:00 | Inference using R |[Slides](https://cosmos-datascience.github.io/slides/week01/2026-qmds/Lab-5-Inference-R.html#/title-slide)-->|

</div>
		





<button class="accordion">Day 6 &#9679; July 13 &#9679; Linear regression </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 12:00 | Introduction to linear regression  |<!--[Slides](https://cosmos-datascience.github.io/slides/week01/06-linear-regression-Quarto.html)-->|
| 1:00 - 2:00 |          | |

</div>


<button class="accordion">Day 7 &#9679; July 14 &#9679; Logistic regression </button>
<div class="panel">

| Time          | Topic                              | Links |
|---------------|------------------------------------|-------|
| 09:00 - 12:00 | Introduction to logistic regression  | <!--[Slides](https://cosmos-datascience.github.io/slides/week02/02a-logit-Quarto.html) -->|
</div>
		


	
	
```{r}
htmltools::tagList(
  htmltools::tags$script(src = "https://d3js.org/d3.v4.min.js"),
  htmltools::tags$script(src = "https://cdnjs.cloudflare.com/ajax/libs/dimple/2.3.0/dimple.latest.min.js")
)
```

```{js, class.source = "jsvis1"}
var acc = document.getElementsByClassName("accordion");
var i;

for (i = 0; i < acc.length; i++) {
  acc[i].addEventListener("click", function() {
    /* Toggle between adding and removing the "active" class,
    to highlight the button that controls the panel */
    this.classList.toggle("active");

    /* Toggle between hiding and showing the active panel */
    var panel = this.nextElementSibling;
    if (panel.style.display === "block") {
      panel.style.display = "none";
    } else {
      panel.style.display = "block";
    }
  });
}
```
